---
title: "Fortune 500 v.s. Non-fortune 500" 
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = F, 
                      message = F)
library(tidyverse)
library(readr)
library(rvest)
library(stringr)
library(tidytext)
library(wordcloud)
library(RColorBrewer)
library(treemap)
library(plotly)
library(packcircles) # bubble plot

theme_set(theme_bw())
```


```{r read_data}
# Read data
datascience <- read_csv("./data/ds_500.csv")
```

### Minimum Requirement of Degree

```{r, dpi = 300}
## minimum requirement of degree
pattern_hi = "[Hh]igh [Ss]chool"
pattern_ba = "[Bb]achelor | \\bB\\.?A\\b | \\bB\\.?S\\b | [Cc]ollege | [Dd]egree"
pattern_ma = "[Mm]aster[^y] | [Aa]dvanced | \\bM\\.?[SA]\\b | [Gg]raduate"
pattern_phd = "\\b[Pp][Hh]\\.?[Dd]\\b | \\bM\\.?D\\b | \\b[Dd]octoral\\b"
```

```{r message = FALSE}
datascience_OR <- datascience %>% 
  mutate(high_school = ifelse(str_detect(.$description, pattern_hi) == TRUE, 1, 0),
         bachelor = ifelse(str_detect(.$description, pattern_ba) == TRUE, 1, 0),
         master = ifelse(str_detect(.$description, pattern_ma) == TRUE, 1, 0), 
         phd = ifelse(str_detect(.$description, pattern_phd) == TRUE, 1, 0), 
         other = high_school + bachelor + master + phd) %>% # if other == 0, means non degree has been found
  mutate(flag = ifelse(flag == 1, "top500", "non_top500"), 
         flag = as.factor(flag), 
         other = ifelse(other == 0, 1, 0)) %>% # if other == 0, means non degree has been found
  gather(key = degree, value = indicator, high_school:other) %>% 
  count(flag, degree, indicator != 0) %>% 
  filter(`indicator != 0` == "TRUE") %>% 
  select(-`indicator != 0`) %>% 
  spread(key = flag, value = n)

datascience_OR %>% 
  mutate(degree = str_to_title(degree),
         degree = recode(degree, High_school = "High School")) %>% 
  mutate(
    non_top500_odds = (non_top500) / sum(datascience$flag == 0),
    top500_odds  = (top500) / sum(datascience$flag == 1),
    log_OR = log(top500_odds / non_top500_odds)
  ) %>% 
  mutate(pos_log_OR = ifelse(log_OR > 0, "Fortune 500 > Non-fortune 500", "Non-fortune 500 > Fortune 500")) %>% 
  mutate(degree = fct_reorder(degree, log_OR)) %>%
  ggplot(aes(degree, log_OR, fill = pos_log_OR)) +
  geom_col() +
  coord_flip() +
  xlab("Degree") +
  ylab("log odds ratio") +
  scale_fill_manual("", values = c("Fortune 500 > Non-fortune 500" = "steelblue", "Non-fortune 500 > Fortune 500" = "black"))
```


High school, master, bachelor, and Ph.D. degree are mentioned more frequently among fortune 500 corporations than non-fortune 500 corporations. “Other” means that the job descriptions do not contain information of degree, and this category falls more frequently in Non-fortune 500 corporations.

<br/>

### Related Academic Background

```{r, dpi = 300}
pattern_bg = c("[Cc]omputer [Ss]cience | \\bC\\.?S\\b | [Mm]achine [Ll]earning | \\bM\\.?L\\b", 
                 "[Ss]tatistic", 
                 "[Mm]ath", 
                 "[Qq]uantitative", 
                 "[Ee]conomic", 
                 "[Bb]iolog", 
                 "[Bb]iostatis", 
                 "[Dd]ata [Ss]cience | \\bD\\.?S\\b", 
                 "[Cc]hemical [Ee]ngineering")
name_bg = c("computer science", 
          "statistics", 
          "mathematics", 
          "quantitative", 
          "economics", 
          "biology", 
          "biostatistics", 
          "data science", 
          "engineer")

bg_freq = data.frame(
  background = pattern_bg, 
  index = name_bg, 
  freq_total = rep(0, length(pattern_bg)), 
  top500 = rep(0, length(pattern_bg)), 
  nontop500 = rep(0, length(pattern_bg)) 
)

for (i in c(1:length(pattern_bg))) {
  bg_freq$freq_total[i] = sum(str_detect(datascience$description, as.character(bg_freq$background[i])))
  bg_freq$top500[i] = sum(str_detect(datascience$description[which(datascience$flag == 1)], as.character(bg_freq$background[i])))
  bg_freq$nontop500[i] = sum(str_detect(datascience$description[which(datascience$flag == 0)], as.character(bg_freq$background[i])))
}

# log odds ratio
bg_freq %>% 
  select(index, top500, nontop500) %>% 
  mutate(
    non_top500_odds = (nontop500) / sum(datascience$flag == 0),
    top500_odds  = (top500) / sum(datascience$flag == 1),
    log_OR = log(top500_odds / non_top500_odds)
  ) %>% 
  mutate(pos_log_OR = ifelse(log_OR > 0, "Fortune 500 > Non-fortune 500", "Non-fortune 500 > Fortune 500")) %>% 
  mutate(
    index = str_to_title(index),
    index = fct_reorder(index, log_OR)
    ) %>%
  ggplot(aes(index, log_OR, fill = pos_log_OR)) +
  geom_col() +
  coord_flip() +
  xlab("Academic Background") +
  ylab("log odds ratio") +
  scale_fill_manual("", values = c("Fortune 500 > Non-fortune 500" = "firebrick3", "Non-fortune 500 > Fortune 500" = "black"))
```

Non-fortune 500 corporations mention Biostatistics, Engineer, Biology more frequently in their job posts, while employees with background in Computer Science and Mathemetics are more preferable to fortune 500 corporations.

<br/>

### Programming / Statistical Tools

```{r}
# Extract tool variable
tool_new = datascience %>% 
  mutate(
    python = ifelse(str_detect(.$description,  c("\\b[Pp][Yy][Tt][Hh][Oo][Nn]\\b")) == TRUE, 1, 0),
    excel = ifelse(str_detect(.$description,  c("\\b[Ee][Xx][Cc][Ee][Ll]\\b")) == TRUE, 1, 0),
    r = ifelse(str_detect(.$description,  c("\\b[Rr]\\b")) == TRUE, 1, 0),
    sql = ifelse(str_detect(.$description,  c("\\b[Ss][Qq][Ll]\\b")) == TRUE, 1, 0),
    java = ifelse(str_detect(.$description,  c("\\b[Jj][Aa][Vv][Aa]\\b")) == TRUE, 1, 0),
    tableau = ifelse(str_detect(.$description,  c("\\b[Tt][Aa][Bb][Ll][Ee][Aa][Uu]\\b")) == TRUE, 1, 0),
    sas = ifelse(str_detect(.$description,  c("\\b[Ss][Aa][Ss]\\b")) == TRUE, 1, 0),
    matlab =  ifelse(str_detect(.$description,  c("\\b[Mm][Aa][Tt][Ll][Aa][Bb]\\b")) == TRUE, 1, 0),
    c = ifelse(str_detect(.$description,  c("\\b[Cc]\\b")) == TRUE, 1, 0),
    perl = ifelse(str_detect(.$description,  c("\\b[Pp][Ee][Rr][Ll]\\b")) == TRUE, 1, 0), 
    scala = ifelse(str_detect(.$description,  c("\\b[Ss][Cc][Aa][Ll][Aa]\\b")) == TRUE, 1, 0), 
    spark = ifelse(str_detect(.$description,  c("\\b[Ss][Pp][Aa][Rr][Kk]\\b")) == TRUE, 1, 0), 
    hadoop = ifelse(str_detect(.$description,  c("\\b[Hh][Aa][Dd][Oo][Oo][Pp]\\b")) == TRUE, 1, 0), 
    aws = ifelse(str_detect(.$description,  c("\\b[Aa][Ww][Ss]\\b")) == TRUE, 1, 0),
    hive = ifelse(str_detect(.$description,  c("\\b[Hh][Ii][Vv][Ee]\\b")) == TRUE, 1, 0),
    tensorflow = ifelse(str_detect(.$description,  c("\\b[Tt][Ee][Nn][Ss][Oo][Rr][Ff][Ll][Oo][Ww]\\b")) == TRUE, 1, 0),
    linux = ifelse(str_detect(.$description,  c("\\b[Ll][Ii][Nn][Uu][Xx]\\b")) == TRUE, 1, 0)
    )
```


```{r fig.width = 10, fig.height = 8}
# Tool - log odds ratio
tool_new %>% 
  gather(key = tool, value = value, python:linux) %>%
  filter(value == 1) %>% 
  count(flag, tool) %>% 
  mutate(
    flag = as.factor(flag),
    flag = ifelse(flag == 1, "top500", "non_top500"),
    tool = str_to_title(tool),
    tool = recode(tool, "C" = "C/C++", "Sql" = "SQL", "Sas" = "SAS", "Aws" = "AWS")
         ) %>% 
  spread(key = flag, value = n) %>% 
  mutate(
    non_top500_odds = (non_top500) / sum(datascience$flag == 0),
    top500_odds  = (top500) / sum(datascience$flag == 1),
    log_OR = log(top500_odds / non_top500_odds)
    ) %>% 
  mutate(pos_log_OR = ifelse(log_OR > 0, "Fortune 500 > Non-fortune 500", "Non-fortune 500 > Fortune 500")) %>% 
  mutate(tool = fct_reorder(tool, log_OR)) %>%
  ggplot(aes(tool, log_OR, fill = pos_log_OR)) +
  geom_col() +
  coord_flip() +
  xlab("Tool") +
  ylab("log odds ratio") +
  scale_fill_manual("", values = c("Fortune 500 > Non-fortune 500" = "orange", "Non-fortune 500 > Fortune 500" = "black"))
```

Excel, followed by Tableau and SQL are more required by non-fortune 500 corporations, while fortune 500 corporations are more likely to prefer applicants with high-level programming tool, such as Perl, C/C++, and Java.


<br/>

### Rquired Skills 

Extract skill variable and plot

```{r fig.width = 12, fig.height = 8}
# Extract skill variable and plot
skill_new = datascience %>%
  mutate(
    machine_learning = ifelse(str_detect(.$description,  c("[Mm]achine [Ll]earning")) == TRUE, 1, 0),
    deep_learning = ifelse(str_detect(.$description,  c("[Dd]eep [Ll]earning")) == TRUE, 1, 0),
    # Data Manipulation & Analysis
    data_mani_ana = ifelse(str_detect(.$description,  c("[Dd]ata [Aa]nalysis|[Dd]ata [Mm]anipulation|[Dd]ata [Mm]anagement|[Dd]ata [Ee]valuation|[Ss]tatistical [Aa]nalysis|[Rr]egression")) == TRUE, 1, 0),
    # data visualization
    data_visul = ifelse(str_detect(.$description,  c("[Dd]ata [Vv]isualization")) == TRUE, 1, 0),
    data_mining = ifelse(str_detect(.$description,  c("[Dd]ata [Mm]ining")) == TRUE, 1, 0),
    modeling = ifelse(str_detect(.$description,  c("[Mm]odeling")) == TRUE, 1, 0),
    # include machine learning optimization, data optimization, mathematical optimization???
    optimization = ifelse(str_detect(.$description,  c("[Oo]ptimization")) == TRUE, 1, 0),
    # interpersonal skills
    interpersonal = ifelse(str_detect(.$description,  c("[Ii]nterpersonal [Ss]kill|[Cc]ommunication|[Ll]istening [Ss]kill|[Tt]eam [Ww]orking|[Nn]egotiation|[Ee]motional [Ii]ntelligence|[Cc]onflict [Rr]esolution|[Pp]roblem [Ss]olving|[Dd]ecision [Mm]aking")) == TRUE, 1, 0),
    # artifical intelligence
    arti_inte = ifelse(str_detect(.$description,  c("\\bAI\\b|[Nn]eural [Nn]etwork")) == TRUE, 1, 0),
    writing = ifelse(str_detect(.$description,  c("[Ww]riting")) == TRUE, 1, 0)
  )
```


```{r fig.width = 12, fig.height = 8}
# Skills - log odds ratio
skill_new %>% 
  gather(key = skill, value = value, machine_learning:writing) %>%
  filter(value == 1) %>% 
  count(flag, skill) %>% 
  mutate(
    flag = as.factor(flag),
    flag = ifelse(flag == 1, "top500", "non_top500")
         ) %>% 
  spread(key = flag, value = n) %>% 
  cbind(skills = c("Artificial Intelligence", "Data Manipulation & Analysis", "Data Mining", "Data Visualization", "Deep Learning", "Interpersonal Skills", "Machine Learning", "Modeling", "Optimization", "Writing Skills")) %>% 
  select(skills, 2, 3) %>% 
  mutate(
    non_top500_odds = (non_top500) / sum(datascience$flag == 0),
    top500_odds  = (top500) / sum(datascience$flag == 1),
    log_OR = log(top500_odds / non_top500_odds)
    ) %>% 
  mutate(pos_log_OR = ifelse(log_OR > 0, "Fortune 500 > Non-fortune 500", "Non-fortune 500 > Fortune 500")) %>% 
  mutate(skills = fct_reorder(skills, log_OR)) %>%
  ggplot(aes(skills, log_OR, fill = pos_log_OR)) +
  geom_col() +
  coord_flip() +
  xlab("Skills") +
  ylab("log odds ratio") +
  scale_fill_manual("", values = c("Fortune 500 > Non-fortune 500" = "springgreen4", "Non-fortune 500 > Fortune 500" = "black"))

```

Writing skills, followed by data visualization, and data manipulation & analysis are more required by non-fortune 500 corporations, while data mining, machine learning, artificial intelligence, deep learning, and modeling are much more preferable to fortune 500 corporations. It makes sense that non-fortune 500 corporations just require employees to master general skills and elementary data science skills, while fortune 500 corporations desire their employees to master more advanced and professional data science skills.
