---
title: "read data from Indeed"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(rvest)
library(stringr)
library(tidytext)
theme_set(theme_bw())
```

### objective

degree

major



### read data (existing)

```{r}
datascience <- read_csv("./data/datascience_market/alldata.csv") %>% 
  filter(!is.na(position))

dim(datascience)

head(datascience)

str(datascience)
```

### tidy datascience data

minimum requirement of degree

```{r}
pattern_Hi = "[Hh]igh [Ss]chool"
pattern_Ba = "[Bb]achelor | \\WB\\.?A\\W | \\WB\\.?S\\W | [Cc]ollege | [Dd]egree"
pattern_Ma = "[Mm]aster[^y] | [Aa]dvanced | \\WM\\.?[SA]\\W | [Gg]raduate"
pattern_Phd = "\\W[Pp][Hh]\\.?[Dd]\\W | \\WM\\.?D\\W"

datascience %>% 
  mutate(degree = ifelse(str_detect(.$description, pattern_Hi) == TRUE, "high school",
                      ifelse(str_detect(.$description, pattern_Ba) == TRUE, "bachelor",
                          ifelse(str_detect(.$description, pattern_Ma) == TRUE, "master",
                               ifelse(str_detect(.$description, pattern_Phd) == TRUE, "phd", "other"))))) %>% 
  mutate(degree = factor(degree, levels = c("high school", "bachelor", "master", "phd", "other"))) %>% 
  ggplot(aes(x = degree)) + geom_bar()

datascience_degree <- datascience %>% 
  mutate(degree = ifelse(str_detect(.$description, pattern_Hi) == TRUE, "high school",
                      ifelse(str_detect(.$description, pattern_Ba) == TRUE, "bachelor",
                          ifelse(str_detect(.$description, pattern_Ma) == TRUE, "master",
                               ifelse(str_detect(.$description, pattern_Phd) == TRUE, "phd", "other"))))) %>% 
  mutate(degree = factor(degree, levels = c("high school", "bachelor", "master", "phd", "other"))) 
```

related background:

```{r}
major <- tibble(major_name = c("Computer Science", "Statistics", "Mathematics", "Quantitative", 
                               "Biology", "Economics", "Data Science", "Chemical Engineering", "Biostatistics"))
                
datascience %>% 
  filter(str_detect(description, "[Mm]athematics") == TRUE)


datascience %>% 
  filter(str_detect(description, "[Cc]omputer [Ss]cience") == TRUE)

datascience %>% 
  filter(str_detect(description, "[Dd]ata [Ss]cience") == TRUE)

```

skill:

```{r}

```


### word frequency count

Took 100 samples from 7000

```{r}
datascience <- mutate(datascience, index = 1:nrow(datascience))
set.seed(1)
sample1 <- sample(1:nrow(datascience), 100, replace = FALSE)
sample1

data_100 <- datascience[sample1,]
```

we’ll un-nest the tokens (i.e. words) in each description; the result is a tidy dataset in which each word is contained within a separate row.

word frequency in description

1. Single word 

```{r}
inspection_words_single = 
  datascience %>% 
  unnest_tokens(word, description)


data(stop_words)

keep_letter_stop_words <- stop_words %>% filter(!word %in% c("C", "c", "R", "r"))

inspection_words_single = 
  anti_join(inspection_words_single, keep_letter_stop_words)

inspection_words_single %>% 
  count(word, sort = TRUE) %>% 
  top_n(50) %>% 
  mutate(word = fct_reorder(word, n)) %>% 
  ggplot(aes(x = word, y = n)) + 
  geom_bar(stat = "identity", fill = "blue", alpha = .6) + 
  coord_flip()
```

2. Double word

```{r}
inspection_words = 
  datascience %>% 
  unnest_tokens(word, description)


data(stop_words)

keep_letter_stop_words <- stop_words %>% filter(!word %in% c("C", "c", "R", "r"))

inspection_words = 
  anti_join(inspection_words, keep_letter_stop_words)


inspection_words %>%
  nest(word) %>%
  mutate(text = map(data, unlist), 
         text = map_chr(text, paste, collapse = " ")) %>% 
  select(-data) %>% 
  unnest_tokens(word, text, token = "ngrams", n = 2) %>% 
  count(word, sort = TRUE) %>% 
  top_n(30) %>% 
  mutate(word = fct_reorder(word, n)) %>% 
  ggplot(aes(x = word, y = n)) + 
  geom_bar(stat = "identity", fill = "blue", alpha = .6) + 
  coord_flip()
```

3. Three words

```{r}
inspection_words %>%
  nest(word) %>%
  mutate(text = map(data, unlist), 
         text = map_chr(text, paste, collapse = " ")) %>% 
  select(-data) %>% 
  unnest_tokens(word, text, token = "ngrams", n = 3) %>% 
  count(word, sort = TRUE) %>% 
  top_n(50) %>% 
  mutate(word = fct_reorder(word, n)) %>% 
  ggplot(aes(x = word, y = n)) + 
  geom_bar(stat = "identity", fill = "blue", alpha = .6) + 
  coord_flip()
```


position word frequency

```{r}
inspection_words_position = 
  datascience %>% 
  unnest_tokens(word, position)

inspection_words

data(stop_words)

#keep_letter_stop_words <- stop_words %>% filter(!word %in% c("C", "c", "R", "r"))

inspection_words_position = 
  anti_join(inspection_words_position, stop_words)

inspection_words_position %>% 
  count(word, sort = TRUE) %>% 
  top_n(10) %>% 
  mutate(word = fct_reorder(word, n)) %>% 
  ggplot(aes(x = word, y = n)) + 
  geom_bar(stat = "identity", fill = "blue", alpha = .6) + 
  coord_flip()

```


Comparing words across groups







